---
title: "Homework 3 - Question 2"
author: "Nickhil Sethi"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, width.cutoff=50)
library(ggplot2)
library(printr)
library(gridExtra)
library(faraway)
```


Load pima dataset:
```{r}
data("pima")
```
## 2.a
One thing that seems unbelievable about this plot -- there seem to be a very large number of zeros on the insulin variable, both for positive and negative tests. This suggests to me either a coding error or 0 representing missing data.
```{r}
ggplot(pima, aes(x=insulin, fill=factor(test))) + 
geom_histogram(
  alpha=.6, position="dodge", binwidth=10)
```

## 2.b
Without the incredible zero values, insulin appears to have a poisson distribution with mean conditional on the test outcome:
```{r}
pima$insulin[pima$insulin == 0] <- NA
ggplot(pima, aes(x=insulin, fill=factor(test))) + geom_histogram(position="dodge", binwidth=10)
```

## 2.c
Let's plot the other values and inspect for any suspect zero values: 
```{r}
g1 <- ggplot(pima, aes(x=glucose, fill=factor(test))) + geom_histogram(position="dodge", binwidth=10)

g2 <- ggplot(pima, aes(x=bmi, fill=factor(test))) + geom_histogram(position="dodge", binwidth=5)

g3 <- ggplot(pima, aes(x=diabetes, fill=factor(test))) + geom_histogram(position="dodge", binwidth=.1)

g4 <- ggplot(pima, aes(x=triceps, fill=factor(test))) + geom_histogram(position="dodge", binwidth=.1)

g5 <- ggplot(pima, aes(x=age, fill=factor(test))) + geom_histogram(position="dodge", binwidth=.1)

g6 <- ggplot(pima, aes(x=pregnant, fill=factor(test))) + geom_histogram(position="dodge", binwidth=.1)

g7 <- ggplot(pima, aes(x=diastolic, fill=factor(test))) + geom_histogram(position="dodge", binwidth=.1)

grid.arrange(g1, g2, g3, g4, g5, g6, g7, ncol=2)
```

It seems the following variables have incredible zeros:
```{r}
pima$glucose[pima$glucose == 0] <- NA
pima$bmi[pima$bmi == 0] <- NA
pima$triceps[pima$triceps == 0] <- NA
pima$diastolic[pima$diastolic == 0] <- NA
nrow(pima)
```
Now let's fit a model. It seems 374 of the  768 rows in $pima$ had some `NA` value and therefore were not included in the regression.
```{r}
lmod <- glm(test ~ pregnant + glucose + diastolic + triceps
          + insulin + bmi + diabetes + age, family=binomial, pima)
sumary(lmod)
nrow(pima)
```
```{r}
lmod2 <- glm(test ~ pregnant + glucose + diastolic 
          + bmi + diabetes + age, family=binomial, pima)
sumary(lmod2)
```
Deviance of lmod2 - lmod2 
```{r}
diff <- deviance(lmod2) - deviance(lmod)
diff
1 - pchisq(diff, 2)
```

Now let's compare based on AIC, using the $step$ command, starting from the largest possible model $lmod$
```{r}
# required to get step to 
# work without error
pima_omit_na <- na.omit(pima)
lmod <- glm(test ~ pregnant + glucose + diastolic + triceps
          + insulin + bmi + diabetes + age, family=binomial, pima_omit_na)
lmodr <- step(lmod, trace=0)
sumary(lmodr)
```
As we can see, $pregnant$, $bmi$, $diabetes$, and $age$ are selected as predictors (although it's noteworthy that the p-value on $pregnant$ is doesn't pass significance). 392 data points are used in the final model.

## f)

```{r}
# let's add a column 
# to the dataframe representing
# if the row has any missing values at all
pima$has_missing <- !complete.cases(pima)

# now let's regress test 
# on has_missing is slight and 
# the p-value of .3 indicates
# the relationship is uncertain
lmod_missing_values <- glm(
  test ~ as.numeric(has_missing), 
  family=binomial, pima)

sumary(lmod_missing_values)

# plotting this relationship,
# we can see visually there isn't much of a 
# correlation between the two variables
plot(jitter(as.numeric(has_missing), .5) ~ jitter(test, .5),  pima)

# now let's include the model
lmod_handle_missing <- glm(
  test ~ pregnant + glucose + diastolic + triceps
          + insulin + bmi + diabetes + age + as.numeric(has_missing),
  family=binomial, pima)
sumary(lmod_handle_missing)
```
